Parameter estimation in biochemical models

### 2017-12-05 Paper_v7.tex
updating authors

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={asg242@cornell.edu}   % email address
]{\fnm{Adithya} \snm{Sagar}}
\author[
   addressref={aff1},
   email={ril34@cornell.edu}
]{\fnm{Rachel} \snm{LeCover}}
\author[
   addressref={aff1},
   email={jdv27@cornell.edu}
]{\inits{D}\fnm{Jeffrey} \snm{Varner}}
\author[
   addressref={aff2},
   email={jdv27@cornell.edu}
]{\fnm{Christine} \snm{Shoemaker}}

@@

\subsection*{Additional file S8-(Comparison of functional values)}
\begin{figure}
\includegraphics[width=1.00\textwidth]{./rachelfigs/compare_functional_vals-crop}
    \caption{Variability  analysis in best objective value for $\mathcal{T}$ = 25 trials. (a) Ackley  300 dimensional (b) Rastrigin 300 dimensional (c) CHO model (d) coagulation. }%
    \label{fig-DOPS-Variability}%
\end{figure}

>>>>

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}                       % id of corresponding address, if any
   noteref={n1},                        % id's of article notes, if any
   email={asg242@cornell.edu}   % email address
]{\fnm{Adithya} \snm{Sagar}}
\author[
   addressref={aff1},
   email={ril34@cornell.edu},
   noteref={n1}
]{\fnm{Rachel} \snm{LeCover}}
\author[
   addressref={aff1},
   corref={aff1},
   email={jdv27@cornell.edu}
]{\inits{D}\fnm{Jeffrey} \snm{Varner}}
\author[
   addressref={aff2},
   email={jdv27@cornell.edu}
]{\fnm{Christine} \snm{Shoemaker}}

@@

\subsection*{Additional file S8-(Comparison of functional values)}
\begin{figure}
\includegraphics[width=1.0\textwidth]{./rachelfigs/compare_functional_vals-crop}
    \caption{Variability  analysis in best objective value for $\mathcal{T}$ = 25 trials. (a) Ackley  300 dimensional (b) Rastrigin 300 dimensional (c) CHO model (d) coagulation. }%
    \label{fig-DOPS-Variability}%
\end{figure}
